---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# galileantools

<!-- badges: start -->
<!-- badges: end -->

The goal of galileantools is to provide tools for applying Galilean transformations, 
simulating projectile motion from moving platforms, estimating platform velocity, 
and visualizing results.

## Overview

`galileantools` provides utilities to:
- apply Galilean transformations,
- simulate projectiles launched from a moving platform (with measurement noise),
- estimate platform velocity (and projectile initial conditions),
- visualize trajectories and diagnostics,
- include a tutorial vignette and an optional Shiny demo.


## Installation

You can install the development version of galileantools like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
# after pushing to GitHub:
# install remotes if needed
# install.packages("remotes")
remotes::install_github("Ourbani237/galileantools")
# for local development:
# update documentation
devtools::document()
# install locally
devtools::install()

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(galileantools)
## basic example code

dat <- simulate_projectile(u0 = c(5,12), pos0 = c(0,1.5),
                           t = seq(0,2.5,0.05), v_platform = 15)

est <- estimate_platform_velocity(dat, known_u_x = 5)
print(paste("Estimated v:", round(est$v_est, 2)))

plots <- plot_trajectories(dat, model_par = c(u_x=5, u_y=12, v=15, h=1.5))
plots$plot_x
plots$plot_y
```

## References / Help

For full documentation of functions, see the vignette:

vignette("tutorial", package = "galileantools")

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
